\LARGE \bf Machine Translation for Tibetan Buddhist Texts

### 2021-04-06 paper/main.tex
Update main.tex
Updated .tex with (most) citations plus Jacob's changes

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

First, we acknowledge that it would be improper to consider our translations as genuine scripture. No matter what our results are, we authors are not in a qualified position to declare something as an honest translation of a Tibetan Buddhist text. To that end, what we have done is pass our results on to someone who can give a more qualified opinion of the accuracy of our translation an so we asked a Native Tibetan Speaker who holds a Master's degree in Buddhist theology and philosophy to  assess our results. This approach was inspired by Bird's paper [citation:Decolonizing NLP ] which suggests including a "human in the loop" as a key step in the process to decolonizing NLP research.

@@

\subsection{Model Design}

@@

\section{Results}

(TODO)

@@

(TODO)

@@

\bibitem{c1} G. O. Young, ``Synthetic structure of industrial plastics (Book style with paper title and editor),'' 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15--64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123--135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ``An approach to graphs of linear forms (Unpublished work style),'' unpublished.
\bibitem{c5} E. H. Miller, ``A note on reflector arrays (Periodical styleÑAccepted for publication),'' IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, ``Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),'' IEEE J. Quantum Electron., submitted for publication.
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),'' IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740--741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, ``Infrared navigationÑPart I: An assessment of feasibility (Periodical style),'' IEEE Trans. Electron Devices, vol. ED-11, pp. 34--39, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ``A clustering technique for digital communications channel equalization using radial basis function networks,'' IEEE Trans. Neural Networks, vol. 4, pp. 570--578, July 1993.
\bibitem{c12} R. W. Lucky, ``Automatic equalization for digital communication,'' Bell Syst. Tech. J., vol. 44, no. 4, pp. 547--588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, ``On the compatibility of adaptive controllers (Published Conference Proceedings style),'' in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8--16.
\bibitem{c14} G. R. Faulhaber, ``Design of service systems with priority reservation,'' in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3--8.
\bibitem{c15} W. D. Doyle, ``Magnetization reversal in films with biaxial anisotropy,'' in 1987 Proc. INTERMAG Conf., pp. 2.2-1--2.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, ``Radio noise currents n short sections on bundle conductors (Presented Conference Paper style),'' presented at the IEEE Summer power Meeting, Dallas, TX, June 22--27, 1990, Paper 90 SM 690-0 PWRS.
\bibitem{c17} J. G. Kreifeldt, ``An analysis of surface-detected EMG as an amplitude-modulated noise,'' presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
\bibitem{c18} J. Williams, ``Narrow-band analyzer (Thesis or Dissertation style),'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
\bibitem{c19} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, ``Nonlinear resonant circuit devices (Patent style),'' U.S. Patent 3 624 12, July 16, 1990.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

@@

First, we acknowledge that it would be improper to consider our translations as genuine sutras. No matter what our results are, we authors are not in a qualified position to declare something as an honest translation of a Tibetan Buddhist text. To that end, what we have done is pass our results on to someone who can give a more qualified opinion of the accuracy of our translation an so we asked a Native Tibetan Speaker who holds a Master's degree in Buddhist theology and philosophy to  assess our results. This approach was inspired by Bird's paper [citation:Decolonizing NLP ] which suggests including a "human in the loop" as a key step in the process to decolonizing NLP research.

@@

\subsection{Model Design}
We used a 6 layer Transformer model that used a multi headed attention mechanism and a switchout transform. Each layer of the transformer model can be divided into an encoder and decoder layer. The encoding layer consists first of a self attention layer, an attention aspect which focuses on the encoded sentence, and then outputs to a feed forward layer. The multi part of the multi headed attention means that each head will encode the information in parallel and then the results will be concatenated and passed to the decoder. Figure one demonstrates this process.
\includegraphics[scale=.4]{Transformer.png}
\caption{\\Figure 1: Overview of a Transformer model}
\\
\par
To prevent overfitting and to augment the data, we added in a switchout transform which will randomly switch out words in the source and target sentence. This also has the added advantage of augmenting the data even further which is especially important for our problem as religious tibetan has a relatively small corpus, around 30 thousand words. We also attempted to use masking, however we found it to be ineffective. Masking hides tokens from the model by replacing the tokens with a <mask> token. Tibetan tokens are not separated in the same way that latin languages separate their tokens. For example,
\begin{verbatim}
“བྱང་ཆུབ་མངོན་པར་རྫོགས་པར་འཚང་རྒྱ་སྟེ།” 
\end{verbatim}
a line in our test corpus translates to “Having the altruistic intention of excellent bodhicitta.” The tibetan word is only one token. Therefore, the mask would not help the model learn at all, as the entire sentence would be marked as <mask> and there would not be enough context for our model to discover the meaning. As a result, we did not use any form of masking in our model. Switchout does not create the same problem as their is always a token to take its place. \par
After implementing our transformer model with switchout we tuned hyper parameters to maximize our Transformer model. We manually tuned the following hyperparameters: dropout, label smoothing, rnn size, the number of transformer layers and the number of heads of the attention model. The final configuration used can be found in the appendix. \par
We used four different metrics to evaluate our results: accuracy, predicted score, perplexity and bilingual evaluation understudy (BLEU). The validation accuracy tells us how well we are learning our training data, the predicted score tells us the average log likelihood for each word, the perplexity tells us how well the model predicts the data and the bleu score evaluates the quality of the translation. Together, these metrics provide us with a decent picture of how well our model is performed.

\section{Results}
\begin{tabular}{ |c| c| c| c| }
 Validation & Ave. Pred. Score & PPL & BLEU \\ 
 40.32\% & -1.69 & 5.41 & 23.01\% \\

\end{tabular}\\

@@

\section{Discussion}

(Kelsey)

@@

@@

\bibitem{c1} Cai Z. (2015) A Method for the Chinese-Tibetan Machine Translation System’s Syntactic Analysis. In: Wong W. (eds) Proceedings of the 4th International Conference on Computer Engineering and Networks. Lecture Notes in Electrical Engineering, vol 355. Springer, Cham.

\bibitem{c2} Liu, H., Zhao, W., Yu, X., & Wu, J. (2016). A Chinese to Tibetan Machine Translation System with Multiple Translating Strategies. Himalayan Linguistics, 15(1).

\bibitem{c3} Hill, Nathan & Meelen, Marieke. (2017). Segmenting and POS tagging Classical Tibetan using a Memory-Based Tagger. Himalayan Linguistics. 16. 10.5070/H916234501.

\bibitem{c4} Faggionato, Christian  and Meelen, Marieke. (2019). Developing the Old Tibetan Treebank. INCOMA Ltd. Proceedings of the International Conference on Recent Advances in Natural Language Processing (RANLP 2019) 304--312

\bibitem{c5} Orna Almogi, Lena Dankin, Nachum Dershowitz, Lior Wolf. A Hackathon for Classical Tibetan.Journal of Data Mining and Digital Humanities, Episciences.org, 2019, Special Issue on Computer-Aided Processing of Intertextuality in Ancient Languages. hal-01371751v3

\bibitem{c6} Orna Almogi, Lena Dankin, Nachum Dershowitz, Lior Wolf. A Hackathon for Classical Tibetan.Journal of Data Mining and Digital Humanities, Episciences.org, 2019, Special Issue on Computer-Aided Processing of Intertextuality in Ancient Languages. hal-01371751v3
